On Secure Delegation of SampBQP with a Classical Client

### 2020-04-03 qpip.tex
Fix bug

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	\Ethan{Think about notation... maybe $s$? typeof($A$) is strange. Also an error here.}
	That is, there exists some $\rho=\sum_j w_j\rho_j^{\otimes m+1}$
	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
	such that for all quantum-classical channels $\Lambda_i$ on $n+T+\frac{T}{\varepsilon}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

@@

	First suppose $p_j<\frac{1}{2}-2\kappa$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	\Ethan{Delete the following and just say it's standard application of Chernoff bound}
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$

@@

	Now, for the other case, $j\notin J$, by \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$
	\Ethan{Trace distance notation}

	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $\poly(\varepsilon)$ due to the padding,
	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point. \Ethan{get rid of the remaining polys}

>>>>

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	That is, there exists some $\rho=\sum_j w_j\rho_j^{\otimes m+1}$
	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
	such that for all quantum-classical channels $\Lambda_i$ on $n+T+\frac{T}{\varepsilon}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

@@

	First suppose $p_j<\frac{1}{2}-2\kappa$,
	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.

@@

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$
	\Ethan{Trace distance notation}

	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $O(\varepsilon)$ due to the padding,
	so the data register has $1-O(\varepsilon)$ probability to be $C(x)$ at this point.
